### 2019-07-01 README.Rmd
Updated README

```{r pathEnrich, warning=FALSE}
# run pathEnrich using kegg_rno
## Genes of interest
sig_pe <- pathEnrich(gk_obj = kegg, gene_list = geneLists$sigGenes)
## Background
bkg_pe <- pathEnrich(gk_obj = kegg, gene_list = geneLists$background)
knitr::kable(head(sig_pe),
             caption = "Table 1. Head of sig_pe dataframe generated using pathEnrich", row.names = FALSE) %>%
  kableExtra::kable_styling(bootstrap_options = c("striped", "hover", "condensed"), full_width = T)
```

@@

```{r pathEnrich_description, echo=FALSE}
# get column names
names <- colnames(sig_pe)
# Define column names
description <- c("KEGG ID",
                 "KEGG pathway description",
                 "PLACE HOLDER",
                 "PLACE HOLDER",
                 "Total number of pathways in KEGG release",
                 "PLACE HOLDER",
                 "PLACE HOLDER",
                 "Unadjusted p-value from Fisher's Exact test",
                 "False Discovery Rate (FDR)")
# Make dataframe
df1 <- data.frame(names, description)
colnames(df1) <- c("Column Names", "Column Description")

knitr::kable(df1,
             caption = "Table 2. Description of columns is dataframe generated by pathEnrich", row.names = FALSE) %>%
  kableExtra::kable_styling(bootstrap_options = c("striped", "hover", "condensed"), full_width = F)
```

@@

The diffEnrich function will merge the results from the *pathEnrich* calls generated above. Specifically, the data frame
'sig_pe' and the data frame 'bkg_pe' will be merged using the base *merge* functionality and be merged by the following columns:
'c("KEGG_ID", "KEGG_description", "KEGG_cnt", "numTested")'. This merged data set will then be used to perform differential 
enrichment using the same method and p-value calculation as described above.

```{r diffEnrich}
## Perform differential enrichment
diff_enrich <- diffEnrich(sig_pe = sig_pe, bkg_pe = bkg_pe)

knitr::kable(head(diff_enrich),
             caption = "Table 2. Description of columns is dataframe generated by pathEnrich", row.names = FALSE) %>%
  kableExtra::kable_styling(bootstrap_options = c("striped", "hover", "condensed"), full_width = F)
```

The result of the *diffEnrich* call is the merged data frame with the estimated odds ration generated by the Fisher's Exact test 
and the associated p-value.

>>>>

```{r pathEnrich, warning=FALSE}
# run pathEnrich using kegg_rno
## List 1
list1_pe <- pathEnrich(gk_obj = kegg, gene_list = geneLists$list1)
## list2
list2_pe <- pathEnrich(gk_obj = kegg, gene_list = geneLists$list2)
```

```{r pathEnrich_kable, warning=FALSE, echo=FALSE}
knitr::kable(head(list1_pe),
             caption = "Table 1. Head of list1_pe data frame generated using pathEnrich", row.names = FALSE) %>%
  kableExtra::kable_styling(bootstrap_options = c("striped", "hover", "condensed"), full_width = T)
```

@@

```{r pathEnrich_description, echo=FALSE}
# get column names
names <- colnames(list1_pe)
# Define column names
description <- c("KEGG Pathway Identifier",
                 "Description of KEGG Pathway (provided by KEGG)",
                 "Number of Genes in KEGG Pathway",
                 "Number of Genes from gene list in KEGG Pathway",
                 "Number of Genes in KEGG Database",
                 "Number of Genes from gene list in KEGG Database",
                 "Expected number of genes from list to be in KEGG pathway by chance (i.e., not enriched)",
                 "P-value for enrichment of list genes related to KEGG pathway",
                 "False Discovery Rate (Benjamini and Hochberg) to account for multiple testing across KEGG pathways")
# Make dataframe
df1 <- data.frame(names, description)
colnames(df1) <- c("Column Names", "Column Description")
```

```{r pathEnrich_vars_kable, warning=FALSE, echo=FALSE}
knitr::kable(df1,
             caption = "Table 2. Description of columns is dataframe generated by pathEnrich", row.names = FALSE) %>%
  kableExtra::kable_styling(bootstrap_options = c("striped", "hover", "condensed"), full_width = F)
```

@@

The diffEnrich function will merge the results from the *pathEnrich* calls generated above. Specifically, the data frame
'list1_pe' and the data frame 'list2_pe' will be merged using the base *merge* functionality and be merged by the following columns:
'c("KEGG_PATHWAY_ID", "KEGG_PATHWAY_description", "KEGG_PATHWAY_cnt", "KEGG_DATABASE_cnt")'. This merged data set will then be used to perform differential enrichment using the same method and p-value calculation as described above. Users do have the option of choosing a method 
for multiple testing adjustment.

```{r diffEnrich}
## Perform differential enrichment
diff_enrich <- diffEnrich(list1_pe = list1_pe, list2_pe = list2_pe, method = 'none')
```

```{r diffEnrich_kable, warning=FALSE, echo=FALSE}
knitr::kable(head(diff_enrich),
             caption = "Table 3. Description of columns is data frame generated by diffEnrich", row.names = FALSE) %>%
  kableExtra::kable_styling(bootstrap_options = c("striped", "hover", "condensed"), full_width = F)
```

The result of the *diffEnrich* call is the merged data frame with the estimated odds ration generated by the Fisher's Exact test 
and the associated p-value. Users can choose from those supported by *stats::p.adjust*, and the defualt is the False Discovery Rate (Benjamini and Hochberg).
